\documentclass[12pt,letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small Informed Consent -- DCE-BCS-2026-001}
\fancyhead[R]{\small Version 1.0 | February 2026}
\fancyfoot[C]{\small Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}

\begin{document}

\begin{center}
{\Large\bfseries INFORMED CONSENT FORM}\\[0.3cm]
{\large Research Study: Understanding Women's Preferences\\for Breast Cancer Screening Programs}\\[0.3cm]
{\normalsize Protocol Number: DCE-BCS-2026-001}\\[0.2cm]
{\normalsize Version 1.0 --- February 12, 2026}
\end{center}

\vspace{0.5cm}
\noindent\rule{\textwidth}{1pt}
\vspace{0.3cm}

\noindent\textbf{Principal Investigator:} [PI Name], [Degree(s)]\\
\textbf{Department:} [Department of Health Economics and Outcomes Research]\\
\textbf{Institution:} [University Name]\\
\textbf{Address:} [University Address]\\
\textbf{Phone:} [Phone Number]\\
\textbf{Email:} [Email Address]\\[0.3cm]
\textbf{Co-Investigators:} [Co-PI Names]\\
\textbf{Sponsor:} [Funding Source]

\vspace{0.5cm}

\section*{1. Introduction}

You are being invited to participate in a research study. This form provides information about the study so you can make an informed decision about whether to participate. Please read this form carefully and ask questions about anything you do not understand before deciding whether to participate.

Your participation is \textbf{entirely voluntary}. You may choose not to participate or to stop participating at any time without penalty or loss of benefits to which you are otherwise entitled.

\section*{2. Purpose of the Study}

The purpose of this study is to understand women's preferences for different breast cancer screening programs. Breast cancer screening can vary in several ways, including the type of test used, how often it is performed, the cost, and the accuracy of results. By understanding which features of screening programs matter most to women, this research aims to help healthcare providers and policymakers design screening programs that better align with patients' values and preferences.

This study uses a method called a \textbf{Discrete Choice Experiment (DCE)}, in which you will be shown pairs of hypothetical screening programs and asked which one you would prefer. There are no right or wrong answers --- we are interested only in your personal preferences.

\section*{3. Study Procedures}

If you agree to participate, you will be asked to:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Complete an online survey} that takes approximately \textbf{20--25 minutes}.
  \item The survey has four sections:
  \begin{itemize}
    \item \textbf{Part A:} Questions about your experience with breast cancer screening (5 minutes)
    \item \textbf{Part B:} 12 choice tasks where you compare pairs of hypothetical screening programs and choose the one you prefer (10--12 minutes)
    \item \textbf{Part C:} Questions about your background, health, and demographics (3--5 minutes)
    \item \textbf{Part D:} Brief questions about your experience completing the survey (2 minutes)
  \end{itemize}
  \item You will complete the survey \textbf{one time only}. There are no follow-up sessions.
\end{enumerate}

\noindent The screening programs described in the survey are \textbf{hypothetical} --- they are not real programs being offered to you, and your responses will not affect your actual healthcare.

\section*{4. Eligibility}

To participate in this study, you must:
\begin{itemize}[leftmargin=*]
  \item Be female (sex assigned at birth)
  \item Be between 40 and 74 years of age
  \item Reside in the United States
  \item Be able to read and understand English
  \item Not currently be receiving treatment for breast cancer
\end{itemize}

\section*{5. Risks and Discomforts}

The risks of participating in this study are \textbf{minimal}. Possible risks include:

\begin{itemize}[leftmargin=*]
  \item \textbf{Mild psychological discomfort:} Some questions ask about breast cancer, family history of cancer, and cancer risk. These topics may cause mild anxiety or emotional discomfort for some participants.
  \item \textbf{Fatigue:} The choice tasks require concentration, which may cause mild mental fatigue.
  \item \textbf{Loss of confidentiality:} Although unlikely, there is a small risk that your responses could be linked to your identity. We take extensive precautions to protect your privacy (see Section 8).
\end{itemize}

\noindent If you experience distress related to breast cancer, we encourage you to contact:
\begin{itemize}
  \item National Cancer Institute Cancer Information Service: 1-800-4-CANCER (1-800-422-6237)
  \item National Breast Cancer Foundation: \url{https://www.nationalbreastcancer.org}
  \item Your primary care provider
\end{itemize}

\section*{6. Benefits}

There are \textbf{no direct benefits} to you from participating in this study. However, your responses will contribute to research that may help improve breast cancer screening programs and health policy decisions for women in the future.

\section*{7. Compensation}

You will receive the following compensation for completing the survey:

\begin{itemize}[leftmargin=*]
  \item \textbf{Online panel participants (Prolific):} \$5.00 paid through the Prolific platform upon verified survey completion
  \item \textbf{Online panel participants (MTurk):} \$4.00 base payment + \$1.00 bonus for quality responses, paid through the Amazon MTurk platform
  \item \textbf{Clinic-based participants:} \$15.00 gift card provided upon survey completion
  \item \textbf{Community participants:} \$10.00 Amazon gift card upon survey completion
\end{itemize}

\noindent If you withdraw from the study before completing the survey, you will receive partial compensation proportional to the portion completed, at the discretion of the research team.

\section*{8. Confidentiality and Privacy}

We will take the following steps to protect your privacy:

\begin{itemize}[leftmargin=*]
  \item The survey does \textbf{not} collect your name, address, Social Security number, or any other directly identifying information.
  \item Your survey responses will be identified only by a randomly assigned participant ID number.
  \item Platform identifiers (Prolific ID, MTurk Worker ID) are used solely for compensation purposes and will be permanently deleted after payment is processed.
  \item All data will be stored on password-protected, encrypted servers maintained by [University Name].
  \item Only authorized members of the research team will have access to the data.
  \item Results will be reported only in aggregate form. No individual responses will be identifiable in any publications or presentations.
  \item De-identified data may be shared with other researchers for future studies, in accordance with journal and funder data-sharing policies.
  \item Data will be retained for a minimum of 7 years following study completion, as required by institutional policy, and then securely destroyed.
\end{itemize}

\noindent The [University Name] Institutional Review Board (IRB) and regulatory authorities may review study records to ensure proper conduct of the research.

\section*{9. Voluntary Participation and Withdrawal}

Your participation in this study is completely voluntary. You have the right to:

\begin{itemize}[leftmargin=*]
  \item Decline to participate without any penalty
  \item Withdraw from the study at any time by closing your browser
  \item Skip individual questions that you do not wish to answer (except choice tasks in Part B, which are required for data analysis)
  \item Request that your data be deleted after participation, by contacting the PI within 30 days of completing the survey
\end{itemize}

\noindent Your decision to participate or not will have no effect on your healthcare, employment, or relationship with [University Name].

\section*{10. Contact Information}

If you have questions, concerns, or complaints about this study, please contact:

\begin{itemize}[leftmargin=*]
  \item \textbf{Principal Investigator:} [PI Name] at [phone] or [email]
  \item \textbf{Research Team:} [Research coordinator name] at [phone] or [email]
\end{itemize}

\noindent If you have questions about your rights as a research participant, or if you have concerns or complaints that you wish to address to someone other than the research team, please contact:

\begin{itemize}[leftmargin=*]
  \item \textbf{Institutional Review Board:} [University Name] Office of Research Compliance\\
  Phone: [IRB phone number]\\
  Email: [IRB email]
\end{itemize}

\section*{11. Statement of Consent}

\noindent I have read this consent form (or it has been read to me). I have had the opportunity to ask questions and have had them answered to my satisfaction. I understand the purpose, procedures, risks, and benefits of this study. I voluntarily agree to participate in this research study.

\vspace{0.5cm}

\noindent\textbf{For online participants:}

\vspace{0.3cm}
\noindent By clicking ``I agree to participate'' below, you are indicating that:
\begin{itemize}[leftmargin=*]
  \item You have read and understood this consent form
  \item You meet the eligibility criteria described above
  \item You voluntarily agree to participate in this study
  \item You are at least 40 years of age
\end{itemize}

\vspace{0.5cm}
\begin{center}
\fbox{\parbox{6cm}{\centering\vspace{0.3cm}\textbf{$\square$ I agree to participate}\vspace{0.3cm}}}
\hspace{2cm}
\fbox{\parbox{6cm}{\centering\vspace{0.3cm}\textbf{$\square$ I do not agree to participate}\vspace{0.3cm}}}
\end{center}

\vspace{1cm}

\noindent\textbf{For clinic-based participants (paper version):}

\vspace{0.5cm}
\noindent\begin{tabular}{p{0.45\textwidth}p{0.1\textwidth}p{0.35\textwidth}}
\rule{0.45\textwidth}{0.4pt} & & \rule{0.35\textwidth}{0.4pt} \\
Participant Signature & & Date \\[1cm]
\rule{0.45\textwidth}{0.4pt} & & \rule{0.35\textwidth}{0.4pt} \\
Participant Name (printed) & & \\[1cm]
\rule{0.45\textwidth}{0.4pt} & & \rule{0.35\textwidth}{0.4pt} \\
Person Obtaining Consent (Signature) & & Date \\[1cm]
\rule{0.45\textwidth}{0.4pt} & & \\
Person Obtaining Consent (printed) & & \\
\end{tabular}

\vspace{1cm}
\noindent\rule{\textwidth}{1pt}

\vspace{0.3cm}
\noindent{\small\textit{You will receive a copy of this signed consent form for your records.}}

\vspace{0.3cm}
\noindent{\small\textit{This study has been reviewed and approved by the [University Name] Institutional Review Board (IRB Protocol \#[Number], approved [Date]).}}

\end{document}
